\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fontspec}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{multicol} % For multi-column achievements

\setmainfont{Roboto} % Using Roboto font

% Colors for section titles
\definecolor{sectioncolor}{HTML}{2C5364}

% Formatting for section titles
\titleformat{\section}{\large\bfseries\color{sectioncolor}}{}{0em}{}[\titlerule]

% Formatting for subsections
\titleformat{\subsection}{\normalsize\bfseries\color{sectioncolor}}{}{0em}{}

% Hyperlink styling
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}

% Start of the document
\begin{document}

% Name and Contact Information
\begin{center}
    {\LARGE \textbf{Vinay Reddy Kalluri}} \\[0.2cm]
    \small
    \href{mailto:vinayreddykalluri@gmail.com}{\texttt{vinayreddykalluri@gmail.com}} \quad | \quad 
    \texttt{+1 (660) 492-8656} \quad | \quad 
    \href{https://www.linkedin.com/in/vinayreddykalluri/}{\texttt{linkedin.com/in/vinayreddykalluri}} \quad | \quad 
    \href{https://github.com/vinayreddykalluri}{\texttt{github.com/vinayreddykalluri}} \quad | \quad 
    \texttt{Atlanta, Georgia, USA} \\
\end{center}


% Summary Section
\section*{Summary}
Java Full Stack Developer with 6.5 years of expertise in designing scalable, secure systems. Skilled in cloud-native architectures, AI integration, and end-to-end development for healthcare and productivity. Driven to solve complex challenges with impactful solutions.



% Skills Section
\section*{Technical Skills}
\begin{tabular}{@{}p{5.5cm}p{12cm}@{}}
\textbf{Programming Languages:}  & Java, Python, Dart, JavaScript, TypeScript \\
\textbf{Frameworks and Libraries:} & Spring Boot, Hibernate, Kafka, Mockito, JUnit, Flutter, RxJS \\
\textbf{Web Technologies:}       & HTML, CSS, Angular, Bootstrap, Tailwind CSS \\
\textbf{Databases:}              & MySQL, PostgreSQL, MongoDB, Oracle \\
\textbf{Cloud Platforms:}        & AWS (EC2, S3, RDS, Lambda), Google Cloud Platform (GCP), Firebase \\
\textbf{DevOps Tools:}           & Git, Jenkins, Docker, GitHub Actions, Kubernetes, CI/CD Pipelines \\
\textbf{AI and Data Science:}    & TensorFlow, Keras, Neural Networks, Prompt Engineering, OpenAI APIs \\
\textbf{Tools and IDEs:}         & IntelliJ IDEA, Postman, Figma, JIRA, Visual Studio Code, Eclipse, PyCharm \\
\textbf{Soft Skills:}            & Problem Solving, Team Collaboration, Agile Methodologies, Strategic Planning \\
\end{tabular}


% Experience Section
\section*{Professional Experience}

% First Job
\noindent\textbf{Developer III \textemdash{} Software Engineering} \hfill \textit{Jan 2024 -- Present} \\
\textit{UST Global Inc, Atlanta, Georgia, USA · Remote} \\
\vspace{-0.4cm}
\begin{itemize}[leftmargin=0.5cm, labelsep=0.3cm, itemsep=0.2em, parsep=0pt, topsep=0pt]
    \item Designed and developed the \textbf{Sales Compensation Incentive System} for Elevance Health using Spring Boot and MySQL, automating broker workflows and enhancing scalability.
    \item Optimized backend systems, reducing processing time by \textbf{20\%} while ensuring compliance with healthcare regulations.
    \item Conducted regular code reviews and implemented scalable architecture, achieving \textbf{99.9\% system uptime}.
    \item Collaborated with stakeholders to align enterprise architecture goals, streamlining cross-team efficiency.
\end{itemize}

\vspace{0.2cm}

% Second Job
\noindent\textbf{Consultant \textemdash{} Software Engineering} \hfill \textit{Mar 2023 -- Jan 2024} \\
\textit{Hays US Corporation, Kansas City, Missouri, USA · Remote} \\
\vspace{-0.4cm}
\begin{itemize}[leftmargin=0.5cm, labelsep=0.3cm, itemsep=0.2em, parsep=0pt, topsep=0pt]
    \item Transitioned monolithic applications to a \textbf{microservices architecture} deployed on AWS, utilizing Spring Boot.
    \item Developed Kafka-based messaging systems to enable \textbf{real-time data synchronization} across distributed services.
    \item Automated infrastructure provisioning using AWS CloudFormation, reducing deployment time by \textbf{50\%}.
    \item Led testing initiatives for distributed systems, ensuring reliability and scalability in high-load environments.
\end{itemize}

\vspace{0.2cm}

% Third Job
\noindent\textbf{Software Engineer \textemdash{} Niche} \hfill \textit{Nov 2019 -- Dec 2021} \\
\textit{Legato Health Technologies, Hyderabad Area, India · On-site} \\
\vspace{-0.4cm}
\begin{itemize}[leftmargin=0.5cm, labelsep=0.3cm, itemsep=0.2em, parsep=0pt, topsep=0pt]
    \item Built enterprise-level applications using Spring Boot, Hibernate, and RESTful APIs, supporting \textbf{millions of daily healthcare transactions}.
    \item Integrated Kafka for real-time messaging and optimized database performance, enhancing query speeds by \textbf{30\%}.
    \item Designed and deployed microservices to replace legacy systems, reducing maintenance costs by \textbf{25\%}.
    \item Collaborated with cross-functional teams to deliver scalable, user-friendly solutions.
\end{itemize}

\vspace{0.2cm}

% Fourth Job
\noindent\textbf{Programmer Analyst} \hfill \textit{Sep 2018 -- Nov 2019} \\
\textit{Cognizant, Hyderabad, India · On-site} \\
\vspace{-0.4cm}
\begin{itemize}[leftmargin=0.5cm, labelsep=0.3cm, itemsep=0.2em, parsep=0pt, topsep=0pt]
    \item Developed REST APIs and web applications using Spring Boot microservices for Anthem Inc, processing \textbf{a million events daily}.
    \item Utilized Spring MVC and Hibernate to implement a robust persistence layer integrated with Oracle and MongoDB.
    \item Contributed to Agile workflows, participating in sprint planning, retrospectives, and bug triaging.
    \item Optimized database queries, significantly reducing system latency by \textbf{40\%}.
\end{itemize}

\vspace{0.2cm}

% Fifth Job
\noindent\textbf{Programmer Analyst Trainee} \hfill \textit{Sep 2017 -- Aug 2018} \\
\textit{Cognizant, Hyderabad, India · On-site} \\
\vspace{-0.4cm}
\begin{itemize}[leftmargin=0.5cm, labelsep=0.3cm, itemsep=0.2em, parsep=0pt, topsep=0pt]
    \item Completed comprehensive training in Full Stack Java Web Development and deployed to the Health Care Business Unit.
    \item Developed web applications using Spring Boot and REST APIs, ensuring smooth integration with legacy systems.
\end{itemize}


\section*{Key Projects}

% First Project
\noindent\textbf{Sales Compensation Incentive System} \hfill \textit{UST Global Inc} \\
\vspace{-0.5em}
\begin{itemize}[leftmargin=0.5cm, labelsep=0.3cm, itemsep=0pt, parsep=0pt, topsep=0pt]
    \item Streamlined broker compensation workflows for Elevance Health by developing a robust system using \textbf{Spring Boot} and \textbf{MySQL}.
    \item Enhanced scalability and compliance, reducing manual intervention by \textbf{40\%}.
\end{itemize}

% Second Project
\noindent\textbf{Drowsiness Detection System} \hfill \textit{VIT University} \\
\vspace{-0.5em}
\begin{itemize}[leftmargin=0.5cm, labelsep=0.3cm, itemsep=0pt, parsep=0pt, topsep=0pt]
    \item Designed an \textbf{AI-powered system} to detect driver fatigue using real-time image streams.
    \item Published findings in an international journal, recognized for innovation in driver safety technology.
\end{itemize}

% Third Project
\noindent\textbf{Friends And Lovers – Mobile Game Application} \hfill \textit{Independent Project} \\
\vspace{-0.5em}
\begin{itemize}[leftmargin=0.5cm, labelsep=0.3cm, itemsep=0pt, parsep=0pt, topsep=0pt]
    \item Developed a cross-platform gaming app using \textbf{Flutter} and \textbf{Firebase}, featuring interactive games like Truth or Dare and Guess the Movie.
    \item Integrated \textbf{Google AdMob} for monetization while ensuring a seamless user experience.
\end{itemize}

% Fourth Project
\noindent\textbf{Keep Motive – Daily Inspirational Quotes App} \hfill \textit{Independent Project} \\
\vspace{-0.5em}
\begin{itemize}[leftmargin=0.5cm, labelsep=0.3cm, itemsep=0pt, parsep=0pt, topsep=0pt]
    \item Created a motivational app delivering curated quotes with a personalized experience.
    \item Designed a \textbf{Flutter-based frontend} and a \textbf{Spring Boot backend} for analytics and recommendations.
   \item Implemented CI/CD pipelines to streamline development and automate testing for efficient updates and improved reliability.
\end{itemize}

% Fifth Project
\noindent\textbf{Couple Nest – Relationship App (In Progress)} \hfill \textit{Independent Project} \\
\vspace{-0.5em}
\begin{itemize}[leftmargin=0.5cm, labelsep=0.3cm, itemsep=0pt, parsep=0pt, topsep=0pt]
    \item Building an innovative app for couples, focused on enhancing emotional connections through features like \textbf{encrypted chat}, \textbf{AI-assisted conflict resolution}, and \textbf{interactive games}.
    \item Leveraging \textbf{Flutter}, \textbf{Spring Boot}, and \textbf{PostgreSQL} for seamless scalability and exceptional user experience.
\end{itemize}

% Education Section
\section*{Education}
\begin{tabularx}{\textwidth}{@{}X@{\hspace{0.5cm}}r@{}}
\textbf{Master of Science in Computer Science} & \textit{Jan 2022 -- May 2023} \\
\textit{University of Missouri - Kansas City (UMKC), USA} & \textit{GPA: 3.9/4.0} \\[0.4cm]

\textbf{Master of Science in Software Engineering} & \textit{Jun 2012 -- May 2017} \\
\textit{VIT University, India} & \textit{GPA: 9.24/10.00 (Gold Medalist, Overall Batch Topper)} \\
\end{tabularx}


% Achievements Section
\section*{Achievements and Awards}
\begin{itemize}[leftmargin=0.5cm, labelsep=0.3cm, itemsep=0.1em, parsep=0pt, topsep=0pt]
    \item \textbf{Secured a \$4000 Research Grant:} Conducted Deep Learning analysis on Phasor Measurement Units (PMU), leveraging Neural Graph Embedding and Convolutional Neural Networks to detect anomalies as a Graduate Research Assistant at UMKC.
    \item \textbf{Winner of UMKC Hack-A-Roo Hackathon:} Developed an innovative Low-Power Image Generation Tool, demonstrating exceptional problem-solving and creativity.
    \item \textbf{Academic Excellence:} Earned multiple Meritorious Awards for outstanding academic performance during the academic year 2016-2017.
    \item \textbf{Gold Medalist at VIT University:} Achieved Overall Batch Topper status (Rank 1) and received the Gold Medal for academic distinction during the MS in Software Engineering program.
    \item \textbf{Best Project Award at Cognizant:} Recognized for designing and implementing a cutting-edge Mobile App – Drowsiness Detection System in 2017.
\end{itemize}


% Research Experience Section
\section*{Research Experience}

\noindent\textbf{Real-time Driver Fatigue or Drowsiness Detection System Using Face Image Stream} \\
\textit{Published in: International Journal of Civil Engineering and Technology (IJCIET)} \\
\vspace{0.2em}
\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Authors:} & Kalluri Vinay Reddy, Ilakiyaselvan, N\\
\textbf{Year:} & 2017 \\
\textbf{Abstract:} & Developed an innovative real-time system to detect driver fatigue using advanced image processing techniques and facial recognition algorithms. The research focuses on improving road safety by identifying early signs of drowsiness and alerting the driver to prevent accidents. \\
\textbf{Published:} & Volume 8, Issue 11, Pages 793–802 \\
\textbf{Access Link:} & \href{https://iaeme.com/Home/article_id/IJCIET_08_11_081}{https://iaeme.com/Home/article\_id/IJCIET\_08\_11\_081}
\end{tabularx}

% End of document
\end{document}